Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-10 qpip0.tex

\begin{lemma}\label{lem:naive-qpip0-binding}[binding property of  Protocol~\ref{proto:qpip0_naive} ]
If a prover's strategy in Protocol~\ref{proto:qpip0_naive} results in passing the testing round with probability $1-\negl(n)$, then conditioning on the Hadamard round being chosen, $\norm{(d,z_{naive})-(d,z_{ideal})}_q \leq O(\eps)$.

, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

>>>>

\begin{lemma}\label{lem:naive-qpip0-binding}[binding property of  Protocol~\ref{proto:qpip0_naive} ]
If a prover's strategy in Protocol~\ref{proto:qpip0_naive} results in passing the testing round with probability $1-\negl(n)$, then conditioning on the Hadamard round being chosen, $\norm{(d,z_{naive})-(d,z_{ideal})}_q \leq O(\eps)$, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

\begin{proof}
By Lemma~\ref{lem:urmila-binding}, if the prover passes the testing round with probability $1-\negl(n)$, there exist a $\rho$ such that $\norm{z_{commit}- M_{XZ}(\rho,h)}_q \leq \negl(n)$. Let $Ver$ be the verification operation run by Protocol~\ref{ProtoQPIP1} on the measurement outcome. \hannote{describe better} Since $Ver$ is an efficient process and $Ver(z_{commmit})=(d,z_{naive})$, we have that

\begin{equation} \label{eq:z=verM}
    \norm{(d,z_{naive})-Ver( M_{XZ}(\rho,h))}_q \leq \negl(n).
\end{equation}
\hannote{actually true with subnormalize shit?}
 By Theorem~\ref{QPIP1thm}, for all $\rho$, 
 \begin{equation}
     \norm{Ver(M_{XZ}(\rho,h))-(d,z_{ideal})}\leq O(\eps).
 \end{equation}
   Combined with Equation~\ref{eq:z=verM} and Lemma~\ref{lem:computational-triangle0}, we have that
   \begin{equation}
       \norm{(d,z_{naive})-(d,z_{ideal})}_q\leq O(\eps)
   \end{equation}
\end{proof}
